---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# meili

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

[Meilisearch](https://meilisearch.com) is a RESTful search API. It aims to be a ready-to-go solution for everyone who wants a fast and relevant search experience.

The goal of the R package `meili` is to provide an R client which is an API wrapper against the `meilisearch` API, see <https://www.meilisearch.com/docs/reference/api/overview>.

## Installation

You can install the development version of meili like so:

``` r
remotes::install_github("KTH-Library/meili")
```

## Environment variables

This package expects two environment variables to be set in `.Renviron`:

MEILI_KEY: The key used to authorize API requests, see [the API docs](https://www.meilisearch.com/docs/learn/security/master_api_keys#communicating-with-a-protected-instance)

MEILI_URL: The public server name where the meilisearch index is accessible

Settings used can be checked using `meili::meili_config(verbose = TRUE)`

## Example

This is a basic example which shows you how to create a search index, retrieve documents from it and finally delete it:

```{r example}
library(meili)
library(dplyr)
library(tibble)

# verify settings

my_config <- meili:::meili_config(verbose = TRUE)

# ingest an in-memory data frame or an on-disk CSV file

co2 <- CO2 |> rownames_to_column(var = "rowid")
task <- meili:::meili_ingest_csv(index = "co2", csvfile = co2)
is_ingested <- meili:::wait_for_status(task$taskUid)

# retrieve three documents from the co2 index
meili:::meili_documents("co2", limit = 3) |> 
  select(-any_of("rowid"))

# run a search for documents matching "quebec 95" w scores > 0.5 (on scale 0..1)
meili:::meili_search("co2", query = "quebec 95") |> 
  filter(`_rankingScore` > 0.5)

# delete the index

task <- meili:::meili_deleteindex("co2")
is_deleted <- meili:::wait_for_status(task$taskUid)


```

## Searching using several queries

To make multiple search queries against the same index:

```{r example2}

meili:::search_name(c("Oscar", "backe"), index = "hrfile") |> 
  select(lastname, unit_name) |> 
  head(6)

```
